Covariant Phase Space via MultiSymplectic Geometry

### 2017-05-16 cpsviams.tex
Sigma graph updated

\section{Introduction: multisymplectic landscape at glance}
Let's briefly recall in what consists the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.

\begin{figure}
  \centering
  \includestandalone[mode=buildnew]{ms_landscape}
  \caption{interesting results}
\end{figure}

@@

\begin{wrapfigure}{L}{0.50\textwidth}
\centering
\includegraphics[width=0.49\textwidth]{Pictures/variations.png}
\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
\end{wrapfigure}
This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\
Therefore, a parametrized regular curve as to be regarded as a family of diffeomerphisms, the flow generated by a vertical tangent field on $F$.\\
The pull-back are there to remark that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$ thus are vertical field of $F$ \underline{along} the section $\phi$.

>>>>

\section{Introduction}
Let's briefly recall in what consists the multisymplectic approach to mechanics of field systems in order to understand its relationship with the covariant phase space approach.

\begin{figure}
  \centering
  \includestandalone[mode=buildnew]{ms_landscape}
  \caption{multisymplectic landscape at glance}
\end{figure}

@@

\begin{wrapfigure}{L}{0.50\textwidth}
\centering
\includegraphics[width=0.49\textwidth]{Pictures/variations.png}
%\caption{\label{fig:variations}Covariant tangent fields as regular variations.}
\end{wrapfigure}

This condition stems from the fact that we want to interpret regular curves on $\Conf$ as smooth variations of field configurations. \\
Therefore, a parametrized regular curve as to be regarded as a family of diffeomerphisms, the flow generated by a vertical tangent field on $F$.\\
The pull-back are there to remark that $T_\phi \Conf$ consists of the infinitesimal smooth variations of $\phi$ thus are vertical field of $F$ \underline{along} the section $\phi$.
